%\addchapter{References}
\addchapter{参考文献}
\begin{thebibliography}{99}% 文献数が10未満の時 {9}，10～99の時 {99}
\bibitem{calinon}
Calinon, Sylvain, Tohid Alizadeh, and Darwin G. Caldwell. "On improving the extrapolation capability of task-parameterized movement models." Intelligent Robots and Systems (IROS), 2013 IEEE/RSJ International Conference on. IEEE, 2013.

\bibitem{ude}
V. Krueger, D. L. Herzog, S. Baby, A. Ude, and D. Kragic, “Learning actions from observations: Primitive-based modeling and grammar,”IEEE Robotics and Automation Magazine, vol. 17,no. 2, pp. 30–43,2010

\bibitem{matsubara}
Matsubara, Takamitsu, Sang-Ho Hyon, and Jun Morimoto. "Learning parametric dynamic movement primitives from multiple demonstrations." Neural Networks 24.5 (2011): 493-500.

\bibitem{sugiura}
杉浦孔明, et al. "Learning, generation and recognition of motions by reference-point-dependent probabilistic models." Advanced Robotics 25.6-7 (2011): 825-848.

\bibitem{sugiura2}
杉浦孔明, and 岩橋直人. "参照点に依存した確率モデルを用いた連続動作の認識と生成." 人工知能学会全国大会論文集 0 (2008): 372-372.

\bibitem{sugiura3}
杉浦孔明, et al. "言語獲得ロボットによる発話理解確率の推定に基づく物体操作対話." 日本ロボット学会誌 28.8 (2010): 978-988.

\bibitem{hmm}
稲邑哲也. "HMM と人間の動作認識・教示・生成." 日本ロボット学会誌 29.5 (2011): 419-422.

\bibitem{dong}
Dong, Shuonan, and Brian Williams. "Learning and recognition of hybrid manipulation motions in variable environments using probabilistic flow tubes." International Journal of Social Robotics 4.4 (2012): 357-368.

\bibitem{nakaoka}
中岡慎一郎, et al. "シンボリックな動作記述を用いた舞踊動作模倣ロボットの実現." 電子情報通信学会技術研究報告. PRMU パターン認識・メディア理解 103.390 (2003): 55-60.

\bibitem{Koenemann}
Koenemann, Jonas, Felix Burget, and Maren Bennewitz. "Real-time imitation of human whole-body motions by humanoids." Robotics and Automation (ICRA), 2014 IEEE International Conference on. IEEE, 2014.

\bibitem{schaal} 
Schaal, Stefan. "Dynamic movement primitives-a framework for motor control in humans and humanoid robotics." Adaptive Motion of Animals and Machines. Springer Tokyo, 2006. 261-280.

\bibitem{imitation1} 
Argall, Brenna D., et al. "A survey of robot learning from demonstration." Robotics and autonomous systems 57.5 (2009): 469-483.

\bibitem{imitation2}
臼井和廉, 波多野拓貴, and 高橋泰岳. "人間による呈示動作のバイアスを用いた人型ロボットの模倣学習." ファジィシステムシンポジウム講演論文集 29 (2013): 836-841.

\bibitem{imitation3}
Eppner, Clemens, et al. "Imitation learning with generalized task descriptions." Robotics and Automation, 2009. ICRA'09. IEEE International Conference on. IEEE, 2009.

\bibitem{imitation4}
Khansari-Zadeh, S. Mohammad, and Aude Billard. "Learning stable nonlinear dynamical systems with gaussian mixture models." Robotics, IEEE Transactions on 27.5 (2011): 943-957.

\end{thebibliography}


