%\addchapter{References}
\addchapter{参考文献}
\begin{thebibliography}{9}% 文献数が10未満の時 {9}，10～99の時 {99}
\bibitem{sugiura}
杉浦孔明, et al. "Learning, generation and recognition of motions by reference-point-dependent probabilistic models." Advanced Robotics 25.6-7 (2011): 825-848.

\bibitem{dong}
Dong, Shuonan, and Brian Williams. "Learning and recognition of hybrid manipulation motions in variable environments using probabilistic flow tubes." International Journal of Social Robotics 4.4 (2012): 357-368.

\bibitem{nakaoka}
中岡慎一郎, et al. "シンボリックな動作記述を用いた舞踊動作模倣ロボットの実現." 電子情報通信学会技術研究報告. PRMU パターン認識・メディア理解 103.390 (2003): 55-60.

\bibitem{Koenemann}
Koenemann, Jonas, Felix Burget, and Maren Bennewitz. "Real-time imitation of human whole-body motions by humanoids." Robotics and Automation (ICRA), 2014 IEEE International Conference on. IEEE, 2014.

\bibitem{schaal} 
Schaal, Stefan. "Dynamic movement primitives-a framework for motor control in humans and humanoid robotics." Adaptive Motion of Animals and Machines. Springer Tokyo, 2006. 261-280.

\bibitem{imitation1} 
Argall, Brenna D., et al. "A survey of robot learning from demonstration." Robotics and autonomous systems 57.5 (2009): 469-483.

\bibitem{imitation2}
臼井和廉, 波多野拓貴, and 高橋泰岳. "人間による呈示動作のバイアスを用いた人型ロボットの模倣学習." ファジィシステムシンポジウム講演論文集 29 (2013): 836-841.

\bibitem{imitation3}
Eppner, Clemens, et al. "Imitation learning with generalized task descriptions." Robotics and Automation, 2009. ICRA'09. IEEE International Conference on. IEEE, 2009.

\bibitem{imitation4}
Khansari-Zadeh, S. Mohammad, and Aude Billard. "Learning stable nonlinear dynamical systems with gaussian mixture models." Robotics, IEEE Transactions on 27.5 (2011): 943-957.

\end{thebibliography}


